\systemnamenospace: Head Orientation-Based Selection\\in Physical Spaces

### 2014-08-14 doc/sui14/abstract.tex
orientation-based rather than head-orientation

%% Yang suggests: Interacting with smart objects in the physical space efficiently is a realistic challenge as these objects become ubiquitous. In this paper, we contribute HOBS, a set of novel methods for selecting physical objects at a distance using infrared-sensed head orientations. We augment a commercial head-worn device, Google Glass, with an infrared (IR) emitter to select targets equipped with IR receivers. We present the iterative design process of our methods, involving a series of interaction technique and hardware design and user evaluations....
Emerging head-worn computing devices can enable interactions with smart objects in physical spaces.
%
We present the iterative design and evaluation of \systemname -- a Head-Orientation Based Method for interacting with these devices at a distance. We augment a commercial wearable device, Google Glass, with an infrared (IR) emitter to select targets equipped with IR receivers. Our first design shows that a naive IR implementation can outperform list selection, but has poor performance when refinement between multiple targets is needed. A second design uses IR intensity measurement at targets to improve refinement. To address the lack of natural mapping of on-screen target lists to spatial target location, our third design infers a spatial data structure of the targets enabling a natural head-motion based disambiguation.
%
Finally, we demonstrate a universal remote control application using HOBS and report qualitative user impressions.

>>>>

%% Yang suggests: Interacting with smart objects in the physical space efficiently is a realistic challenge as these objects become ubiquitous. In this paper, we contribute HOBS, a set of novel methods for selecting physical objects at a distance using infrared-sensed head orientations. We augment a commercial head-worn device, Google Glass, with an infrared (IR) emitter to select targets equipped with IR receivers. We present the iterative design process of our methods, involving a series of interaction technique and hardware design and user evaluations....
Emerging head-worn computing devices can enable interactions with smart objects in physical spaces.
%
We present the iterative design and evaluation of \systemname -- a Head Orientation-Based Selection technique for interacting with these devices at a distance. We augment a commercial wearable device, Google Glass, with an infrared (IR) emitter to select targets equipped with IR receivers. Our first design shows that a naive IR implementation can outperform list selection, but has poor performance when refinement between multiple targets is needed. A second design uses IR intensity measurement at targets to improve refinement. To address the lack of natural mapping of on-screen target lists to spatial target location, our third design infers a spatial data structure of the targets enabling a natural head-motion based disambiguation.
%
Finally, we demonstrate a universal remote control application using HOBS and report qualitative user impressions.

### 2014-08-14 doc/sui14/conclusion.tex
orientation-based rather than head-orientation

In this paper, by presenting our iterative design process in head-orientation based targeting, we have learned that IR alone can help reduce the overall acquisition time by reducing the chances when we need to perform refinement. With IR intensity added, the targeting can work better in a relative dense environment. However, a more natural approach is to combine IR with head motion. Through our preliminary user studies, we learned that this is a more intuitive way of performing refinement in comparison to the menu-based selections. We leave a more comprehensive technical solution of using motion sensors and its evaluation as the future work.

>>>>

In this paper, by presenting our iterative design process in head orientation-based targeting, we have learned that IR alone can help reduce the overall acquisition time by reducing the chances when we need to perform refinement. With IR intensity added, the targeting can work better in a relative dense environment. However, a more natural approach is to combine IR with head motion. Through our preliminary user studies, we learned that this is a more intuitive way of performing refinement in comparison to the menu-based selections. We leave a more comprehensive technical solution of using motion sensors and its evaluation as the future work.

### 2014-08-14 doc/sui14/interaction.tex
bjoern's editing pass
orientation-based rather than head-orientation

%!TEX root = sui14.tex
\section{IR for head orientation-based targeting}
In this section, we present our hardware platform (IR targeting) and interaction model (head-orientation based) that we will use throughout our iterative designs.

@@

\subsection{Interaction Model}
From the user's perspective, interaction with \systemname proceeds in two stages (Figure~\ref{fig:interaction}):

>>>>

%!TEX root = sui14.tex
\section{IR for head orientation-based targeting}
In this section, we present our hardware platform (IR targeting) and interaction model (head orientation-based) that we will use throughout our iterative designs.

@@

\newpage %bjoern hack fix
\subsection{Interaction Model}
From the user's perspective, interaction with \systemname proceeds in two stages (Figure~\ref{fig:interaction}):
